Scaling up the hyperparameter grid for Naomi

### 2023-04-06 src/dev_scale-grid/scale-grid.Rmd
Undo scale grid git mistake #22

@@

## Application to Naomi

Let's apply this PCA approach to the grids for the Naomi model:

>>>>

Verifying the number of grid points used:

```{r}
stopifnot(nrow(quad$modesandhessians) == 2)
```

How are these grid points spaced across the 24 dimensions?^[Note that this section was added in later after in order to build intuitions, and doesn't flow very naturally!]

```{r}
quad$modesandhessians[, 1:24] %>%
  pivot_longer(cols = everything()) %>%
  mutate(id = rep(1:24, times = 2)) %>%
  ggplot(aes(x = reorder(name, id), y = value)) +
    geom_point(alpha = 0.8) +
    labs(x = "", y = "Value") + 
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
```

Interesting to note that for the Cholesky adapted grid with `levels = c(1, 1, ..., 2, 1, ..., 1)` we see variation in all of the dimensions greater than or equal to the 16th.
This is related to the Cholesky adaption being based on a lower triangular matrix.
To verify this, we can look at the differences between the two grid points:

```{r}
diff(as.matrix(quad$modesandhessians[, 1:24]))
```

Let's also verify that adaption is happening as we expect it to be:

```{r}
#' This is what the base grid looks like
mvQuad::getNodes(base_grid)

base_grid_copy <- rlang::duplicate(base_grid)

#' Rescale it according to the mode and Hessian with Cholesky factor
mvQuad::rescale(base_grid, m = quad$optresults$mode, C = Matrix::forceSymmetric(solve(quad$optresults$hessian)), dec.type = 2)

#' Verify that the adapted grid has the same nodes and are used by aghq::aghq
stopifnot(all(mvQuad::getNodes(base_grid) == unname(as.matrix(quad$modesandhessians[, 1:24]))))
```

How would a spectral grid behave with the same choice of `levels`?
Notice that there is a difference for all of the 24 dimenions when `dec.type = 1` (spectral) is used:

```{r}
mvQuad::rescale(base_grid_copy, m = quad$optresults$mode, C = Matrix::forceSymmetric(solve(quad$optresults$hessian)), dec.type = 1)
diff(mvQuad::getNodes(base_grid_copy))
```

@@

## Scoping the application to Naomi

Let's see how large the PCA approach would make the grids for Naomi:
